Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2024-12-20 ms-3/ms.tex
Reveal a strange phenomenon in Fig 1e

\section*{Results and Discussion}
Our estimates of $\theta$ were robust across the population sizes included in the empirical analysis of U.S. counties. 
However, inaccuracies were more common in counties with small populations outside the examined range.%(\nameref{S1_Fig}). 
We found that the LRT method of testing for sharp changes in $\theta$ is also robust across population sizes represented in the empirical data (Fig\ 1 e, f). 
Adequate test performance for the LRT is characterized by an average \( p \)-value of 0.5 when the effect size is zero, with decreasing average $p$-values as the effect size increases.

>>>>

\section*{Results and Discussion}
Our estimates of $\theta$ were robust across the population sizes included in the empirical analysis of U.S. counties. 
However, inaccuracies were more common in counties with small populations outside the examined range.%(\nameref{S1_Fig}). 
We found that the LRT method of testing for sharp changes in $\theta$ is also robust across population sizes represented in the empirical data (Fig\ 1 e, f). 
Adequate test performance for the LRT is characterized by an average $p$-value of 0.5 when the effect size is zero, with decreasing average $p$-values as the effect size increases.
